---
title: "Multiple Factor Analysis"
author: "Jigncheng Xu, Matthew Rainey, Cristian Garay, and Sai Dulla"
date: "November 29, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Multiple Factor Analysis

MFA is used when several sets of variables have been measured on the same set of observations.
The number and/or nature of the variables used to describe the observations can var from one 
set of variables to the other, but the observations should be the same in all the data sets

The goals of MFA:

- to analyze several data sets measured on the same observations
- to provide a set of common factor scores i.e compromise factor scores
- to project each of the original data sets onto the compromise to analyze
  communalities and discrepancies

## The Different Steps of MFA: 

- Step 1: Calculate PCA of each Data Table
- Step 2: Creating the α Weight Vector
- Step 3: Generalized PCA of X
- Step 4: Computing Factor Scores
- Step 5: Computing Partial Factor Scores
- Step 6: Determining the importance of the Tables in the Compromise
- Step 7: Bootstrap

## Step 1: With the MFA package
- 

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

