---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Contributions

We measure the importance of each dimension (or component) by its eigenvalue, which indicates how much of the inertia of the data is explained by that dimension.  To understand how much each observation, variable and table contributes to each dimension, we compute the contribution for each.  All of the contributions for a given dimension must add to one.

With our wine data, each observation is a different wine, each table corresponds to an assessor and each variable is an assessors grade given to the wine on certain criteria. 

### Contribution of an Observation to a Dimension

The contributions of an observation tells us how much each observation contributes to a dimension.  To get the Contributions of an Observation, use the `ContribObs` function.  The output given will have the columns represent dimensions and the rows represent observations.  Using the wine data as an example:
```{r}
library(MFA)
mfa.wines <- mfa(wines, sets)
ctr.obs <- ContribObs(mfa.wines)
ctr.obs[,1:3]
```

Since we have 12 wines (observations), we get a sense of how much an observation contributes by it's contributions size relative to 1/12.  For example, the tenth wine contributes a lot to the second dimension, but very little to the first or third.

###Contributions of a Variable to a Dimension

The contributions of a variable tells us how much each variable contributes to a dimension.  To get the Contributions of a Variable, use the `ContribVar` function. The output has columns representing dimensions and rows representing variables.  With the wine data as an example:
```{r}
ctr.var <- ContribVar(mfa.wines)
ctr.var[1:8, 1:3]
```

We have 53 variables, so we get a sense of how much a variable contributes by it's contributions size relative to 1/53.  For example, the third variable contributes a lot to the second dimension but very little to the third.

###Contributions of a Table to a Dimension

The contribution of a table to tells us how much all of the variables in a given table contribute to a dimension.  To get the Contributions of a Table, use the `ContribTable` function. The output has columns representing dimensions and rows representing Tables.  With the wine data as an example:
```{r}
ctr.table <- ContribTable(mfa.wines)
ctr.table[, 1:3]
```

There are 10 assessors (tables), so we get a sense of how much a table contributes by it's contributions size relative to 1/10.  For example the fifth assessor contributes a lot to the third dimension, but only a small amount to the second.
