---
title: "Performing MFA"
author: "Jingcheng Xu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Performing MFA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This vignette is about using this package to perform MFA (Multiple
Factor Analysis), get summaries for the result, and plot the results.

## Performing MFA
To perform MFA, use the `mfa` function:
```{r}
library(MFA)
result <- mfa(wines, sets)
```
Here `wines` is a data set included in the package, and `sets` is a
list of integer vectors representing the subtables in the `wines` data set.

```{r}
result
```

## Summaries of the eigenvalues
To get the summaries of eigenvalues of the result, we can use the
`EigSummary`:
```{r}
EigSummary(result)
```

## Plotting the results
There are 3 functions that can plot the result.
```{r, fig.width=7, fig.height=7}
PlotFactorScores(result, group = wines$country, label = wines$ID)
PlotPartialFactorScores(result, 1, group = wines$country, label = wines$ID,
                        dim = c(2, 3))
PlotLoadings(result)
```
The `PlotFactorScores` function plot the factor scores of the result
from MFA. The argument `group` can be used to provide grouping
(different colouring) on the plot.

The `PlotPartialFactorScores` function is similar, only requiring one
more argument to specify the particular table.

The `PlotLoadings` function plots the variable loadings. Similar to
the other two functions, `var.group` argument can be used to provide
grouping among variables.

## Related functions
### Contributions
...

### Bootstrap
The package also included a function `BootstrapRatios` for computing
the bootstrap ratios, which can be used to find observations that
reliably contribute to a given component.
```{r}
BootstrapRatios(result, times = 2000)
```
